---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# stockAnalyzer

<!-- badges: start -->
<!-- badges: end -->

This is an R package that provides basic time series modelling functionalities to analyze historical stock prices. Investment in the stock market requires not only knowledge about the listed companies, but also basic summary statistics and modellings of individual stock prices. Given time-series stock price data, this package provides key summary statistics, applies moving average and exponential smoothing models to the data, and visualizes in-sample moving average as well as exponential smoothing fits. A convenient use case for this package is to combine it with the `quantmod` library, which can provide well-formated stock price data from Yahoo Finance dataset with customized date range setting.
## Installation

You can install the released version of stockAnalyzer from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("stockAnalyzer")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("UBC-MDS/stockAnalyzer")
```

## Features

The package contains the following five functions:

- `summaryStats`

This function calculates summary statistics including mean price, minimum price, maximum price, volatility and return rate based on daily historical stock prices.
Users can specify lengths of time spans to calculate summary statistics on, and what kind of stock price measurement to use.

- `movingAverage`

This function applies the moving average model to all measurements of stock price and returns a pandas dataframe containing in-sample fitted values. Users can specify the length of moving average windows (unit: days).

- `exponentialSmoothing`

This function performs exponential smoothing on historical stock price time series data. Users can specify the `alpha` parameter (which defines the weighting, ranging between 0 and 1) for smoothing.

- `visMovingAverage`

This function creates a line chart showing the raw historical data and fitted data using the moving average method. Users are able to specify the dataframe used, the column of choice (such as 'Close', 'Adj Close') for moving average calculation, and the length of moving average window (unit: days).

- `visExpSmoothing`

This function creates a line chart showing the raw historical data and fitted data using the exponential smoothing method. Users are able to specify the dataframe used, the column of choice (such as 'Close', 'Adj Close') for exponential smoothing calculation, and the `alpha` parameter (which defines the weighting, ranging between 0 and 1) for smoothing.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
# Download stock price data
library(quantmod)
getSymbols("AAPL")

library(stockAnalyzer)

moving_avg_AAPL <- movingAverage(AAPL,300,paste("moveAverage", colnames(AAPL), sep="_"))

```

## 